Notes: New gaugings in 3d from three-form

### 2023-06-19 Draft_3dH3.tex
Changes by Emanuel.

%%%%%%%% generalised stuff
\newcommand{\gL}{\mathcal{L}}
\newcommand{\gM}{\mathcal{M}}
\newcommand{\tw}{{\cal U}}
\newcommand{\kr}[2]{\delta^{#1}_{#2}}
\newcommand{\cU}{{\cal U}}
\newcommand{\UI}{\left(U^{-1}\right)}
\newcommand{\flt}[1]{\underline{#1}}
\newcommand{\fl}[1]{\ov{#1}}
\newcommand{\cY}{{\cal Y}}
\newcommand{\vg}{\mathring{g}}
\newcommand{\cP}{{\cal P}}
\newcommand{\cV}{{\cal V}}
\newcommand{\cVI}{\left(\cV^{-1}\right)}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\dg}{\vert g \vert}

@@

%% Comments
\newcommand{\EM}[1]{\textcolor{red}{#1}}
\newcommand{\MG}[1]{\textcolor{blue}{#1}}
\definecolor{darkorange}{RGB}{166, 88, 0}
\newcommand{\CE}[1]{\textcolor{darkorange}{#1}}
\newcommand{\CG}{\Com{G}{\EE}}
\newcommand{\cJ}{{\cal J}}

@@

\begin{titlepage}
	\vfill
	\begin{flushright}
		HU-EP-23/XX
	\end{flushright}

@@

\EM{To do:
\begin{itemize}
	\item Think about title - mention new AdS$_3$ vacua? Lifting AdS$_3$ vacua?
	\item Comment earlier on uplift of 6d gSUGRA
	\item Add references to introduction
	\item Complex geometry of moduli space?
	\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
\end{itemize}
}

@@

Nonetheless, there are half-maximal, i.e. ${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing. These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``large'' and ``small'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux. Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}. Moreover, the string sigma model in these vacua is also integrable \cite{}. Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.

@@

\subsubsection{The $S^3 \times S^3$ truncation} \label{s:S3S3}
Let us first review the dyonic $S^3 \times S^3$ truncation of IIB supergravity \cite{Inverso:2016eet}, which forms the starting point of our construction. The key step in the construction of \cite{Inverso:2016eet} is that we can use the $\SL{4}$ generalised frame \eqref{eq:SLnFrame} to form a generalised Leibniz parallelisation of $\En{7}$ via the embedding
\begin{equation} \label{eq:SL4Embedding}
	\En{7} \rightarrow \SL{8} \rightarrow \SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+ \,.
\end{equation}
The fundamental of $\En{7}$ then decomposes as
\begin{equation} \label{eq:56inSL4SL4}
	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
\end{equation}
where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$. Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the $\SL{4}_1$ and $\SL{4}_2$ must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2016eet}. Thus, we write the 56 $\En{7}$ coordinates as
\begin{equation}
	Y^M = \left( Y^{\cA\cB} ,\, Y_{\cA\cB} \right) \,,
\end{equation}
with $\cA, \cB = 1, \ldots, 8$ labelling the fundamental of $\SL{8}$, corresponding to the decomposition $\En{7} \rightarrow \SL{8}$. Following the conventions of \cite{Inverso:2016eet}, the coordinates of the two $\SL{4}$ ExFTs are embedded as $Y^{IJ} \subset Y^{\cA\cB}$, with $I, J = 1, 2, 3, 8$, and $Y_{AB} \subset Y_{\cA\cB}$, with $A, B = 4, 5, 6, 7$. Solving the $\SL{4}$ ExFT section condition for $Y^{IJ}$ and $Y_{AB}$ guarantees a solution to the $\En{7}$ ExFT, and we choose the solution where the six physical coordinates of IIB are
\begin{equation} \label{eq:PhysicalCoords}
	y^i = Y^{i8},\, \qquad \tilde{y}_a = Y_{a7} \,, \qquad i = 1, 2, 3 \,, \qquad a = 4, 5, 6 \,.
\end{equation}
This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \mathbb{R}^+_1 \subset \SL{4}_1$ and $\SL{3}_2 \times \mathbb{R}^+_2 \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.

@@

IIB supergravity contains an S-duality doublet of 6-forms, which we can easily identify using the decomposition $\En{7} \rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$, under which the $\En{7}$ adjoint decomposes as
\begin{equation} \label{eq:AdjointSL6}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{\left(35,1\right)_0} \oplus \mathbf{\left(1,3\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(1,2\right)_{\pm 6}} \\
		& \quad \oplus \mathbf{\left(\overline{15},2\right)_2} \oplus \mathbf{\left(\overline{15},1\right)_{-4}} \oplus \mathbf{\left(15,2\right)_{-2}} \oplus \mathbf{\left(15,1\right)_4} \,.
	\end{split}
\end{equation}
The 6-form doublet corresponds to the $\mathbf{\left(1,2\right)}_{6}$. To understand if one of the 6-forms in the doublet are singlets under $\SL{4}_1 \times \SL{4}_2 \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4}_1 \times \SL{4}_2$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2$, as defined by the embedding of the physical coordinates in \eqref{eq:PhysicalCoords}. Important for us is the correct identification of the $\mathbb{R}^+$ charges in both decompositions. We have, on the one hand,
\begin{equation} \label{eq:SL4SL4}
	\begin{split}
		\En{7} &\rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2 \times \mathbb{R}^+_{\SL{8}} \,,
	\end{split}
\end{equation}
and, on the other,
\begin{equation} \label{eq:SL6SL2}
	\begin{split}
		\En{7} &\rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_{\SL{2}} \times \mathbb{R}^+_{\SL{6}} \times \mathbb{R}^+_{\rm IIB} \,.
	\end{split}
\end{equation}
Here, we label the $\mathbb{R}^+$'s with a subscript that refers to the the groups they belong to. The $\mathbb{R}^+$ generators of the two decompositions are related as
\begin{equation} \label{eq:R+charges}
	\begin{split}
		\mathbb{R}^+_{\SL{6}} &= - \frac12 \left( \mathbb{R}^+_{\SL{3}_1} + \mathbb{R}^+_{\SL{3}_2} \right) \,, \\
		\mathbb{R}^+_{\SL{2}} &= \frac14 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} + \mathbb{R}^+_{\SL{8}} \right) \,, \\
		\mathbb{R}^+_{\rm IIB} &= \frac12 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} - 3\, \mathbb{R}^+_{\SL{8}} \right) \,.
	\end{split}
\end{equation}

The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+_{\SL{8}}$, given by
\begin{equation}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{63} \oplus \mathbf{70} \\
		&\rightarrow \mathbf{\left(15,1\right)_0} \oplus \mathbf{\left(1,15\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(4,\overline{4}\right)_2} \oplus \mathbf{\left(\overline{4},4\right)_{-2}} \\
		& \quad \oplus \mathbf{\left(1,1\right)_{-4}} \oplus \mathbf{\left(1,1\right)_{4}} \oplus \mathbf{\left(4,\overline{4}\right)_{-2}} \oplus \mathbf{\left(\overline{4},4\right)_{2}} \oplus \mathbf{\left(6,6\right)_0} \,.
	\end{split}
\end{equation}
Using \eqref{eq:R+charges}, we can now identify each of the singlet generators $\left(1,1\right)_{\pm4}$ with one of the $\SL{2}$ doublet generators of charge $\mp 6$. Therefore, we find exactly one singlet $\SL{4}_1 \times \SL{4}_2$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential. The other $\SL{4}_1 \times \SL{4}_2$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not correspond to a different physical field. Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.

@@

\subsection{Adding fluxes to other dyonic truncations}
One could also imagine applying the same procedure we described here to turn on fluxes in other maximally supersymmetric compactifications. Natural candidates are the $S^1$ reductions of the consistent truncations to dyonically gauged 4-dimensional maximal supergravities \cite{Guarino:2015jca,Inverso:2016eet}. The 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively. The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$, as reviewed in \ref{s:SLn}.

In order to use our procedure for turning on a flux we would have to find singlets in the $\mbf{133}$ of $\En{7}$ under $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$ for the respective cases. However, it is straightforward to check that there are no singlets corresponding to a $(p-1)$-form potential in the adjoint of $\En{7}$ under these groups. This also stresses why the $S^3\times S^3$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$. \EM{Needs some thinking -- EM}

@@

\paragraph{}
A particularly interesting family of solutions is obtained in the case $\Omega=\ts{\Omega}=0$, where eq.~\eqref{eq:chiomegapsi} reduces to
\begin{equation} \label{eq:chipsi}
	\begin{split}
		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\[3pt]
		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + e^{2\psi}\,\d z^{2}\,, \\[5pt]
		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,.
	\end{split}
\end{equation}
Again, the deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}. From the 4-dimensional perspective obtained after reducing on $S^3 \times S^3$, these deformations correspond to turning on Wilson lines for the $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ gauge fields along $S^1$. The $\psi$ deformation is even simpler: it just rescales the $S^1$ radius. These $\chi_i$, $\ts{\chi}_i$, $\psi$ deformations are completely analogous to $\mathbb{C}$-structure deformations of $T^2$, with the $\chi_i$, $\ts{\chi}_i$ corresponding to the real part and the $\psi$ deformation to the imaginary part of the $\mathbb{C}$-structure deformation. Note that the $\psi$ deformation does not exist in the otherwise analogous AdS$_4 \times S^5 \times S^1$ vacua in \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, due to the ``S-fold'' identification in that case. This leads to an important difference in the global structure of the moduli space that we will discuss in section \ref{s:Compact}.

@@

Using our consistent truncation and the 3-dimensional potential, we studied the moduli space of the AdS$_3$ vacuum within 3-dimensional gauged supergravity. Even a simple search led to a surprisingly large 11-dimensional moduli space of AdS$_3 \times S^3 \times S^3 \times S^1$ vacua, with more moduli likely. While most of these moduli break all supersymmetries, we also identified submanifolds where ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ is preserved, where the ${\cal N}=4$ cases always correspond to the ``large'' superconformal algebra. The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}. I.e. they correspond to local diffeomorphisms mixing angles on the $S^3$'s with the $S^1$, but which are not globally well-defined, much like complex structure deformations of $T^2$, allowing us to compute the full Kaluza-Klein spectrum of these deformed AdS$_3$ vacua. Generic ``flat deformations'' of this type break all supersymmetries but are still perturbatively stable. Moreover, they are protected against perturbative higher-derivative corrections because the deformations locally correspond to diffeomorphisms.

>>>>

%%%%%%%% generalised stuff
\newcommand{\gL}{\mathcal{L}}
\newcommand{\gM}{\mathcal{M}}
\newcommand{\tw}{{\cal U}}
\newcommand{\kr}[2]{\delta^{#1}_{#2}}
\newcommand{\cU}{{\cal U}}
\newcommand{\UI}{\left(U^{-1}\right)}
\newcommand{\flt}[1]{\underline{#1}}
\newcommand{\fl}[1]{\ov{#1}}
\newcommand{\cY}{{\cal Y}}
\newcommand{\vg}{\mathring{g}}
\newcommand{\cP}{{\cal P}}
\newcommand{\cV}{{\cal V}}
\newcommand{\cVI}{\left(\cV^{-1}\right)}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\dg}{\vert g \vert}
\newcommand{\CG}{\Com{G}{\EE}}
\newcommand{\cJ}{{\cal J}}
\newcommand{\RO}{\mathbb{R}^+_{\SL{3}_1}}
\newcommand{\RT}{\mathbb{R}^+_{\SL{3}_2}}

@@

%% Comments
\newcommand{\EM}[1]{\textcolor{red}{#1}}
\newcommand{\MG}[1]{\textcolor{blue}{#1}}
\definecolor{darkorange}{RGB}{166, 88, 0}
\newcommand{\CE}[1]{\textcolor{darkorange}{#1}}

@@

\begin{titlepage}
	\vfill
	\begin{flushright}
		HU-EP-23/18
	\end{flushright}

@@

\EM{To do:
\begin{itemize}
	\item Periodicity $4\pi$ or $2\pi$
	\item Mention lack of higher-dimensional origin for Berg and Samtleben
	\item Comment earlier on uplift of 6d gSUGRA
	\item Add references to introduction
	%\item Complex geometry of moduli space?
	%\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
\end{itemize}
}

@@

Nonetheless, there are half-maximal, i.e. ${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing. These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``large'' and ``small'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux. Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}. \EM{Cut?} Moreover, the string sigma model in these vacua is also integrable \cite{}. Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.

@@

\subsubsection{The $S^3 \times S^3$ truncation} \label{s:S3S3}
Let us first review the dyonic $S^3 \times S^3$ truncation of IIB supergravity \cite{Inverso:2016eet}, which forms the starting point of our construction. The key step in the construction of \cite{Inverso:2016eet} is that we can use the $\SL{4}$ generalised frame \eqref{eq:SLnFrame} to form a generalised Leibniz parallelisation of $\En{7}$ via the embedding
\begin{equation} \label{eq:SL4Embedding}
	\En{7} \rightarrow \SL{8} \rightarrow \SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+ \,.
\end{equation}
The fundamental of $\En{7}$ then decomposes as
\begin{equation} \label{eq:56inSL4SL4}
	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
\end{equation}
where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$. Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the $\SL{4}_1$ and $\SL{4}_2$ must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2016eet}. Thus, we write the 56 $\En{7}$ coordinates as
\begin{equation}
	Y^M = \left( Y^{\cA\cB} ,\, Y_{\cA\cB} \right) \,,
\end{equation}
with $\cA, \cB = 1, \ldots, 8$ labelling the fundamental of $\SL{8}$, corresponding to the decomposition $\En{7} \rightarrow \SL{8}$. Following the conventions of \cite{Inverso:2016eet}, the coordinates of the two $\SL{4}$ ExFTs are embedded as $Y^{IJ} \subset Y^{\cA\cB}$, with $I, J = 1, 2, 3, 8$, and $Y_{AB} \subset Y_{\cA\cB}$, with $A, B = 4, 5, 6, 7$. Solving the $\SL{4}$ ExFT section condition for $Y^{IJ}$ and $Y_{AB}$ guarantees a solution to the $\En{7}$ ExFT, and we choose the solution where the six physical coordinates of IIB are
\begin{equation} \label{eq:PhysicalCoords}
	y^i = Y^{i8},\, \qquad \tilde{y}_a = Y_{a7} \,, \qquad i = 1, 2, 3 \,, \qquad a = 4, 5, 6 \,.
\end{equation}
This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \RO \subset \SL{4}_1$ and $\SL{3}_2 \times \RT \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.

@@

IIB supergravity contains an S-duality doublet of 6-forms, which we can easily identify using the decomposition $\En{7} \rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$, under which the $\En{7}$ adjoint decomposes as
\begin{equation} \label{eq:AdjointSL6}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{\left(35,1\right)_0} \oplus \mathbf{\left(1,3\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(1,2\right)_{\pm 6}} \\
		& \quad \oplus \mathbf{\left(\overline{15},2\right)_2} \oplus \mathbf{\left(\overline{15},1\right)_{-4}} \oplus \mathbf{\left(15,2\right)_{-2}} \oplus \mathbf{\left(15,1\right)_4} \,.
	\end{split}
\end{equation}
The 6-form doublet corresponds to the $\mathbf{\left(1,2\right)}_{6}$. To understand if one of the 6-forms in the doublet are singlets under $\SL{4}_1 \times \SL{4}_2 \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4}_1 \times \SL{4}_2$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \RO \times \RT$, as defined by the embedding of the physical coordinates in \eqref{eq:PhysicalCoords}. Important for us is the correct identification of the $\mathbb{R}^+$ charges in both decompositions. We have, on the one hand,
\begin{equation} \label{eq:SL4SL4}
	\begin{split}
		\En{7} &\rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \RO \times \RT \times \mathbb{R}^+_{\SL{8}} \,,
	\end{split}
\end{equation}
and, on the other,
\begin{equation} \label{eq:SL6SL2}
	\begin{split}
		\En{7} &\rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_{\SL{2}} \times \mathbb{R}^+_{\SL{6}} \times \mathbb{R}^+_{\rm IIB} \,.
	\end{split}
\end{equation}
Here, we label the $\mathbb{R}^+$'s with a subscript that refers to the the groups they belong to. The $\mathbb{R}^+$ generators of the two decompositions are related as
\begin{equation} \label{eq:R+charges}
	\begin{split}
		\mathbb{R}^+_{\SL{6}} &= - \frac12 \left( \RO + \RT \right) \,, \\
		\mathbb{R}^+_{\SL{2}} &= \frac14 \left( \RO - \RT + \mathbb{R}^+_{\SL{8}} \right) \,, \\
		\mathbb{R}^+_{\rm IIB} &= \frac12 \left( \RO - \RT - 3\, \mathbb{R}^+_{\SL{8}} \right) \,.
	\end{split}
\end{equation}

The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+_{\SL{8}}$, given by
\begin{equation} \label{eq:133DecompSL4SL4}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{63} \oplus \mathbf{70} \\
		&\rightarrow \mathbf{\left(15,1\right)_0} \oplus \mathbf{\left(1,15\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(4,\overline{4}\right)_2} \oplus \mathbf{\left(\overline{4},4\right)_{-2}} \\
		& \quad \oplus \mathbf{\left(1,1\right)_{-4}} \oplus \mathbf{\left(1,1\right)_{4}} \oplus \mathbf{\left(4,\overline{4}\right)_{-2}} \oplus \mathbf{\left(\overline{4},4\right)_{2}} \oplus \mathbf{\left(6,6\right)_0} \,.
	\end{split}
\end{equation}
Using \eqref{eq:R+charges}, we can now identify each of the singlet generators $\left(1,1\right)_{\pm4}$ with one of the $\SL{2}$ doublet generators of charge $\mp 6$. Therefore, we find exactly one singlet $\SL{4}_1 \times \SL{4}_2$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential. The other $\SL{4}_1 \times \SL{4}_2$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not correspond to a different physical field. Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.

@@

\subsection{Adding fluxes to other consistent truncations}
We can also try to apply the same procedure we described here to turn on fluxes in other consistent truncations. One set of natural candidates are the $S^1$ reductions of the consistent truncations to dyonically gauged 4-dimensional maximal supergravities \cite{Guarino:2015jca,Inverso:2016eet}. These 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively. The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{8-p} \times \SL{p}$, with $p = 1,\, 2,\, 3$ for the respective cases, and are constructed as in section \ref{s:SLn}.

Let us see whether we can turn on a similar flux as in the case of $S^3 \times S^3 \times S^1$ for these cases. Here we will consider the case of a flux which has one leg on $S^1$, so as to require the truncation to 3 dimensions. In this case, we can always choose a gauge where the potential is fully on $S^{7-p} \times S^{p-1}$ and depends on the $S^1$ coordinate. Turning on such a flux only leads to a consistent truncation if we can find singlets in the $\mbf{133}$ of $\En{7}$ under $\SL{8-p} \times \SL{p}$ for the respective cases of $S^{7-p} \times S^{p-1}$, $p = 1,\, 2,\, 3$, that correspond to $p$-form potential. And, indeed for all these cases, the $\mbf{133}$ only contains exactly one singlet, corresponding to the $\mathbb{R}^+$ generator that commutes with $\SL{8-p} \times \SL{p}$.

However, this $\mathbb{R}^+$ generator cannot correspond to a form potential. If it did, there would also have be a corresponding compact generator in the same representation (with possibly different $\mathbb{R}^+$ chargse), just as in \eqref{eq:133DecompSL4SL4}, associated to the ``dual'' potential. Since we only have one $\SL{8-p} \times \SL{p}$ singlet, this cannot be a $p$-form potential and, therefore, turning on new fluxes with legs on $S^1$ will not lead to consistent truncation for $S^{7-p} \times S^{p-1} \times S^1$, $p = 1,\, 2,\, 3$. This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, i.e. the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.

Our analysis does not rule out the possibility of adding fluxes whose only legs are on $S^{7-p} \times S^p$, with none on $S^1$. In this case, we could use the analysis above but look for singlets in the $\mathbf{56} \otimes \mathbf{133}$, corresponding to the fluxes on $S^{7-p} \times S^p$.

@@

\paragraph{}
A particularly interesting family of solutions is obtained in the case $\Omega=\ts{\Omega}=0$, where eq.~\eqref{eq:chiomegapsi} reduces to
\begin{equation} \label{eq:chipsi}
	\begin{split}
		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\[3pt]
		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + e^{2\psi}\,\d z^{2}\,, \\[5pt]
		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,.
	\end{split}
\end{equation}
Again, the deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Guarino:2020gfe,Giambrone:2021zvp,Giambrone:2021wsm}. From the 4-dimensional perspective obtained after reducing on $S^3 \times S^3$, these deformations correspond to turning on Wilson lines for the $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ gauge fields along $S^1$. The $\psi$ deformation is even simpler: it just rescales the $S^1$ radius. These $\chi_i$, $\ts{\chi}_i$, $\psi$ deformations are completely analogous to $\mathbb{C}$-structure deformations of $T^2$, with the $\chi_i$, $\ts{\chi}_i$ corresponding to the real part and the $\psi$ deformation to the imaginary part of the $\mathbb{C}$-structure deformation. Note that the $\psi$ deformation does not exist in the otherwise analogous AdS$_4 \times S^5 \times S^1$ vacua in \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, due to the ``S-fold'' identification in that case. This leads to an important difference in the global structure of the moduli space that we will discuss in section \ref{s:Compact}.

@@

Using our consistent truncation and the 3-dimensional potential, we studied the moduli space of the AdS$_3$ vacuum within 3-dimensional gauged supergravity. Even a simple search led to a surprisingly large 11-dimensional moduli space of AdS$_3 \times S^3 \times S^3 \times S^1$ vacua, with more moduli likely. While most of these moduli break all supersymmetries, we also identified submanifolds where ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ is preserved, where the ${\cal N}=4$ cases always correspond to the ``large'' superconformal algebra. The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}. I.e. they correspond to local diffeomorphisms mixing angles on the $S^3$'s with the $S^1$, but which are not globally well-defined, much like complex structure deformations of $T^2$, allowing us to compute the full Kaluza-Klein spectrum of these deformed AdS$_3$ vacua. Generic ``flat deformations'' of this type break all supersymmetries but are still perturbatively stable. Moreover, they are protected against perturbative higher-derivative corrections because the deformations locally correspond to diffeomorphisms.
